\thesistitle

### 2019-07-23 sections/clonerefactor.tex
Better explain type 2R clonerefactor stuff

\subsection{Validating the type 2R variability threshold}
In the definition of type 2R clones (see section \ref{sec:type2r}) we described how type 2R clones work on basis of a variability threshold. This threshold, shown more formally in formula \ref{eq:type2r}, is checked by CloneRefactor. Implementing such a threshold involves some important design decisions, and has a lot of underwater complexity. In this section we explain how CloneRefactor detects type 2R clones on basis of this variability threshold.

@@

Figure \ref{fig:clonerefactort2rflow} shows the steps that CloneRefactor performs to find clones conforming with the type 2R variability threshold. This process is done as a postprocessing step after clone detection. The type 2R clone determination process is described in more detail in section \ref{sec:comparingstuff}. Each of the following paragraphs will explain a step from figure \ref{fig:clonerefactort2rflow}.

@@

The symbols in this equation refer to the symbols of the column headers of table \ref{table:equalityarrays}. When we apply this equation to the example clone classes displayed in figure \ref{fig:equalityarrays}, we get the following sum:

>>>>

\subsection{Validating the type 2R variability threshold}
In the definition of type 2R clones (see section \ref{sec:type2r}) we described how type 2R clones work on basis of a variability threshold. This threshold, shown more formally in formula \ref{eq:type2r}, is checked by CloneRefactor. Implementing such a threshold involves some important design decisions, and has a lot of underwater complexity. In this section we explain how CloneRefactor detects type 2R clones on basis of this variability threshold. This process is done as a postprocessing step after clone detection. The type 2R clone detection process is described in more detail in section \ref{sec:comparingstuff}. In short, this process detects clones allowing for any variability between expressions. This postprocessing step then determines which (parts of) these clones are valid by the configure variability threshold.

@@

Figure \ref{fig:clonerefactort2rflow} shows the steps that CloneRefactor performs to find clones conforming with the type 2R variability threshold. Each of the following paragraphs will explain a step from this figure.

@@

Where \textit{E} refers to the equality arrays shown in table \ref{table:equalityarrays}. When we apply this equation to the example clone classes displayed in figure \ref{fig:equalityarrays}, we get the following sum:
